---
title: 'WORKSHEET #5'
author: "Ann Erika D. Gabales"
date: "2022-11-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. The table shows the enrollment of BS in Compter Science, SY 2010-2011.
*a. Plot the data using a bar graph. Write the codes and copy the result.*
```{r enrollment}
Enrollment <-c(80,75,70,60)
barplot(Enrollment,
        main="BS in Computer Science",
        xlab="Course year",
        ylab="2019-2020",
        names.arg = c("1st", "2nd", "3rd", "4th"))
```
*b. Using the same table, label the barchart with* \
**Title = ” Enrollment of BS Computer Science** \
**horizontal axis = “Curriculum Year”** *and* \
**vertical axis = “number of students”** \
```{r }
Enrollment <-c(80,75,70,60)
barplot(Enrollment,
        main="Enrollment of BS Computer Science",
        xlab="Curriculum Year",
        ylab="number of students",
        names.arg = c("1st", "2nd", "3rd", "4th"),)
```
## 2. The monthly income of De Jesus family was spent on the following:
**60% on Food, 10% on electricity, 5% for savings, and**\
**25% for other miscellaneous expenses.**\
  *a. Create a table for the above scenario. Write the codes and its result.*
```{r expenses}
library(scales)
spent <- c(0.6,0.1,0.05,0.25)

data <- matrix(percent(spent), ncol = 1)
rownames(data) <- c("Food", "Electricity","Savings", "other expenses")
colnames(data) <- c("Spent")

final=as.table(data)
final
```
*b. Plot the data using a pie chart. Add labels, colors and legend. Write the codes and its result.*
```{r pie}
spent <- c(60, 10, 5, 25)

spent_labels <- round(spent/sum(spent) * 100, 1)
spent_labels <- paste(spent_labels, "%", sep = "")

pie(spent,
    main = "Miscellaneous",
    col = rainbow(length(spent)),
    labels = spent_labels,
    cex = 0.8)
legend(1.5, 0.5, c("Food","Electricity","Savings","Other expenses"),
       cex = 0.8, fill = rainbow((length(spent))))
```
## 3. Open the mtcars dataset.
```{r }
data("mtcars")
head(mtcars)
```
*a. Create a simple histogram specifically for mpg (miles per gallon) variable. Use $ to select the mpg only. Write the codes and its result.*
```{r mtcars}
hist(mtcars$mpg)
```
*b. Colored histogram with different number of bins.* \
```{r }
hist(mtcars$mpg, breaks=12, col="red")
```
*c.Add a Normal Curve. Copy the result.*
```{r }
x <- mtcars$mpg
h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon",
        main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)
```
## 4. Open the iris dataset. Create a subset for each species.
```{r }
data("iris")
force(iris)
```
*a. Write the codes and its result.*
```{r }
set_iris <- subset(iris, Species == "setosa")
set_iris

ver_iris <- subset(iris, Species == "versicolor")
ver_iris

vir_iris <- subset(iris, Species == "virginica")
vir_iris
```
*b. Get the mean for every characteristics of each species using colMeans(). Write the codes and its result.*
```{r }
setosa <- colMeans(set_iris[sapply(set_iris,is.numeric)])
setosa

versicolor <- colMeans(ver_iris[sapply(ver_iris,is.numeric)])
versicolor

virginica <- colMeans(vir_iris[sapply(vir_iris,is.numeric)])
virginica
```
*c. Combine all species by using rbind()*
```{r }
species <- rbind(setosa, versicolor, virginica)
species
```
*d.  From the data in 4-c: Create the barplot().Write the codes and its result*
```{r }
barplot(species, beside = TRUE,
        main = "Iris Data",
        xlab = "Characteristics",
        ylab = "Mean Scores",
        col = c("red","green","blue"))

```